# Resume-Latex

Latex code for resume 
format:MIT
Content:Priyanshu Oli

# Code
%-------------------------
% ATS Optimized One Page Resume
% Author : Priyanshu Oli
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}


\pdfgentounicode=1

% Margins (tight & ATS safe)
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.55in}

\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\bfseries
}{}{0em}{}[\titlerule \vspace{-6pt}]

% Commands
\newcommand{\resumeItem}[1]{\item \small{#1}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
\begin{document}

%----------HEADER----------
\begin{center}
    {\Large \textbf{Priyanshu Oli}}\\
    Dehradun, Uttarakhand \\
    +91-7906580231 \quad
    priyanshuoli818@gmail.com \quad
    \href{https://www.linkedin.com/in/priyanshu-oli-17b81a205/}{LinkedIn} \quad
    \href{https://leetcode.com/u/Error_line1/}{LeetCode}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
Aspiring Software Engineer with strong foundations in \textbf{Machine Learning, Data Structures, and Algorithms}. Experienced in NLP-based ML systems and sentiment analysis. Proficient in C++, Python, and core computer science subjects. Seeking ML or Software Development roles.

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeItem{\textbf{B.Tech in Computer Science and Engineering}, Graphic Era Hill University \hfill 2022 -- Present\\
CGPA: 7.81 / 10 \hfill Dehradun, Uttarakhand}
\resumeItem{\textbf{Class XII (CBSE)}, Kendriya Vidyalaya ITBP \hfill 2022 \quad 90.16\%}
\resumeItem{\textbf{Class X (CBSE)}, Kendriya Vidyalaya ITBP \hfill 2020 \quad 93.4\%}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeItem{\textbf{Fake News Detection System} \hfill Apr 2024 -- Jun 2024
\resumeItemListStart
\resumeItem{Built NLP-based ML model to classify news as fake or real.}
\resumeItem{Used text preprocessing, TF-IDF vectorization, and supervised learning.}
\resumeItem{Achieved \textbf{98\% accuracy} using precision, recall, and F1-score.}
\resumeItemListEnd}

\resumeItem{\textbf{Unmasking Fake Applications (Sentiment Analysis)} \hfill Oct 2024 -- Dec 2024
\resumeItemListStart
\resumeItem{Developed sentiment analysis model using user reviews to detect fake apps.}
\resumeItem{Implemented Logistic Regression, SVM, Naive Bayes, and Random Forest.}
\resumeItem{Achieved \textbf{82\% accuracy}, improving app legitimacy detection.}
\resumeItemListEnd}

\resumeItem{\textbf{Mini C Compiler (Group Project)} \hfill Jan 2025 -- Apr 2025
\resumeItemListStart
\resumeItem{Developed Mini C Compiler performing lexical analysis using Lex.}
\resumeItem{Displayed tokenized output using a basic React frontend.}
\resumeItem{Collaborated using Git for version control.}
\resumeItemListEnd}

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{TECHNICAL SKILLS}
\resumeSubHeadingListStart
\resumeItem{\textbf{Programming:} C++, C, Python, JavaScript}
\resumeItem{\textbf{Machine Learning:} TensorFlow, scikit-learn, NLP, Sentiment Analysis}
\resumeItem{\textbf{Web:} HTML, CSS, React (basic)}
\resumeItem{\textbf{Databases:} MySQL}
\resumeItem{\textbf{Core CS:} DSA, OS, DBMS, Computer Networks, Compiler Design}
\resumeItem{\textbf{Tools:} Git, GitHub, MS Office}
\resumeSubHeadingListEnd

%-----------CODING PROFILE-----------
\section{CODING PROFILE}
\resumeSubHeadingListStart
\resumeItem{LeetCode: Solved \textbf{300+ problems} across arrays, strings, trees, graphs, recursion, and DP.}
\resumeItem{GeeksforGeeks: Solved \textbf{80+ problems} focusing on core DSA topics.}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS \& RESPONSIBILITY}
\resumeSubHeadingListStart
\resumeItem{National-level Table Tennis player, represented region in KVS Nationals.}
\resumeItem{SWAYAM NPTEL Certified in Ethical Hacking.}
\resumeItem{NSS Member – demonstrated leadership and teamwork.}
\resumeSubHeadingListEnd

\end{document}
